---
title: "Grade_Analysis_SL"
author: "Sami Louahlia"
format: html
code-fold: true
---
```{r}
#|message: false
here::i_am("r-101-grade-analysis.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
```

### Q1 Data
```{r}
#|message: false
grade <- vroom(here("grades.csv"))
```
### Q2 
```{r}
Q2 <- grade |> summarize("minimum" = min(Exam, na.rm=TRUE), "maxixmum" = max(Exam, na.rm=TRUE), "median" = median(Exam, na.rm=TRUE), "mean" = mean(Exam, na.rm=TRUE))

table2 <- knitr::kable(Q2)
```
This table offers descriptive of the variable Exam
`r table2`

### Q3 
```{r}
NoFinal <- grade |> filter(is.na(Exam)==TRUE)
NoFinalnb <- count(NoFinal)
```
A total of `r NoFinalnb` students did not take the final exam.

### Q4 
```{r}
GradeB <- grade |> filter(!is.na(Exam))
ggplot(GradeB, aes(x = Exam))+
  geom_bar()

```

### Q5 
```{r}
grouped_grade <- grade|> group_by(Group)
 countpergroup <- count(grouped_grade)
 table5<- knitr::kable(countpergroup)
```
This table shows how many people can be found in each groups (here called grp)
`r table5`

### Q6
```{r}
ggplot(grade, aes(x=Group))+
  geom_bar()
```
Here is a graphical representation of the group's number of members.

### Q7
```{r}
ggplot(GradeB, aes(x=Exam, fill=Group))+
  geom_bar()
```
This is visually pleasing. However, it seems rather uninformative :(
```{r}
ggplot(GradeB, aes(x=Exam, fill=Group))+
  geom_bar(position="fill")
```
This makes the group comparable in relative terms. We however lose the absolute grade distribution in the process.

### Q8
```{r}
Q8 <- grade |> group_by(Group) |>
  summarise(Missed_Fin = sum(is.na(Exam)))

table8<- knitr::kable(Q8)
```

The number of students missing the final exam per group is as shown in this table.
`r table8`

### Q9
```{r}
ggplot(Q8,aes(x= Group, y = Missed_Fin)) +
         geom_col()+
xlab("Groups")+
ylab("Nb of skippers")
```

This is a graphical representation of the previous question. 

### Q10 

```{r}
New_Grade <- grade |> pivot_longer(cols = -c(Id, Group),
names_to="Exam_form",
values_to ="Grade")
```

### Q11

```{r}
Q11 <- New_Grade |> group_by(Id) |>
  summarise(Nb_skip = sum(is.na(Grade)))

```

### Q12

```{r}
ggplot(Q11, aes(x=Nb_skip)) +
         geom_bar()
```

This is the distribution of the number of missing grades per students. 

### Q13
Here we try to do get the same info as in Q8, namely the number of students, per group, who missed the Exam

```{r}
Q13 <- New_Grade |> filter(Exam_form=="Exam") |> group_by(Group) |>  summarise(Missed_tests = sum(is.na(Grade)))
table13 <- knitr:: kable(Q13)
```
`r table13`

### Q14

```{r}
Q14 <- New_Grade |> filter(str_starts(Exam_form, "Online")) |> group_by(Id) |>  summarise(Missed_OMCQ = sum(is.na(Grade)))
table14 <- knitr:: kable(Q14)
```

### Q15

```{r}
Q15 <- grade |> rowwise() |> mutate(QSkip=sum(is.na((c_across(starts_with("Online"))))))
ggplot(Q15, aes(x=QSkip, y=Exam))+
  geom_jitter(alpha=0.4, width = 0.1, height= 0.1)
```

This is a graphical representation of the grade of the exam for each students, conditioned on the number of online MCQ skipped. It appears there is some form of negative correlation. The more one skips the MCQs the lower the Exam grade.

```{r}

ggplot(Q15, aes(x=as.factor(QSkip), y=Exam))+
  geom_boxplot()
```
Another way to put it. We can see most of the grades are indeed decreasing as students skip more MCQs.

### Q16

```{r}
Q16 <- Q15 |> group_by(Id) |>
  summarise(QSkip>0)|>
  print(Q16)
```

